Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-04 docs/evol.tex
spell-checked paper; corrected various errors

\author{Dimitris Mitropoulos    \and
       Vassilios Karakoidas	\and
       Georgios Gousios         \and
       Panos Louridas		\and
       Diomidis Spinellis
}
\institute{
       	Department of Management Science and Technology\\
	Athens University of Economics and Business\\
      	\email{\{dimitro, bkarak, louridas, dds\}@aueb.gr}\\
	Software Engineering Research Group\\
	Delft University of Technology\\
	\email{G.Gousios@tudelft.nl}
}

@@

A security bug is a programming error that introduces a potentially
exploitable weakness into a computer system~\cite{SSL12}\cite{TJBD11}. This weakness could lead to a
security breach with unfortunate consequences in different layers, like databases,
native code, applications, libraries and others. Despite the significant
effort to detect and eliminate such bugs~\cite{SZ12}, little attention has been paid to
study them in relation to software evolution~\cite{L96}\cite{LRWPT97}\cite{IB06}\cite{RGMA06}.
In this paper we present how we used a large software ecosystem to analyze
how evolving software packages are related to the different types of security
vulnerabilities.

@@

We chose to focus our study on the security bugs rather than other
software bugs. This is because compared to other bug categories,
the category of security bugs has two distinct features: it is critical~\cite{SZ12}
and it costs~\cite{BCL08}. Specifically, a software bug can
lead to a mulfunction of a software artifact that runs under specific
requirements but a security bug can allow a malicious user to alter the execution
of the entire application for his or her own gain. In this case, such bugs could span a wide
range of security and privacy issues, like viewing sensitive information, the destruction or
modification of sensitive data, denial of service and others.
Moreover, security bug disclosures lead to a negative and significant change
in market value for a software vendor~\cite{TW07}.
Hence, one of the basic pursuits in every new software release should
be the mitigation of such bugs.

The motivation behind our work was to validate if programmers tend to care for
such high-risk bugs when they release a new version of their software. In
addition, we wanted to investigate other critical features associated with such
vulnerabilities like the persistency of a bug. In essence, to check if critical bugs stay
unresolved for a long time. Also, we wanted to elaborate more on the relation of security
bugs not only with performance bugs (as Zaman et al.~\cite{ZAH11} have already
did) but also with other bug categories. In the same manner, we tried to check
the relation between a version's size and its' security bugs knowing the
that research has been contradictory on the the
issue~\cite{BP84}\cite{SYTP85}\cite{NBZ06}\cite{GKMS00}.
Finally, we examined the Maven ecosystem as a whole from a security
perspective. Its structure, gave us the oportunity to see if a project version that is a dependency to
a large number of others contains a high rate of security bugs.
In this case we can strenghten the relationship between Linus' Law and
software security as Meneely et al. have already indicated~\cite{MW10}.

The main contributions of this research are:
\begin{itemize}
	\item The analysis of how security bugs evolve over time. To achieve
this, we inspect every project per version. Our hypothesis is that security
bugs must decrease as a project evolves since they are critical and developers
should eliminate them.
	\item Security bug persistense between versions. We show evidence that
security bugs are not eliminated between versions.
	\item We show evidence of the relation between security bugs and a project
version's size.  Here, size is defined in terms of bytecode.
	\item The correlation of security bugs with other bug categories. We
show evidence on how such bugs are correlated with bugs that have to do with
performance, coding practices and others.
%	\item The relation of software dependencies and security bugs. Our
%hypothesis is that an artifact that is a dependency of many other artifacts
%should have a low rate of security bugs. 
\end{itemize}

@@

Initially, we obtained a snapshot (January 2012) of the Maven repository and
handled it locally to retreive a list of all the names of the project versions
that existed in it. A project version can be uniquely identified by the triplet:
{\it group id}, {\it artifact id} and {\it version}.
Since FindBugs analyzes applications written in the Java
programming language, and the Maven repository
hosts projects from languages other than Java such as Scala, Groovy,
Clojure etc. we filtered out such projects by performing a series of checks in
the repository data and metadata.

@@

The statistical mesurements presented in Table~\ref{tbl:repository}
indicate that we have 17,505 projects and the data set's median
is 3, which means that almost 50\% (8,753 projects) of the project
population has 1 to 3 versions.
Note that the Maven repository has many projects with a
few number of versions. For instance, there are numerous projects with a
number of versions that is less than ten.
There are a few projects containing ten
versions and only a few with hundreds of versions. The maximum number of
versions for a project is 338. The 3$^{rd}$ quartile measurement
also indicated that 75\% (13,129) of the projects have a maximum of 8 versions.

@@

\begin{table}
\centering
\caption{Bug Categorisation According to FindBugs}
\label{tbl:bug-cat}
\begin{tabular}{l p{15em}}
\hline
Category & Description\\
\hline
Bad Practice & Violations of recommended and essential
coding practice. \\
Correctness & Involves coding mistakes resulting in code
that was probably not what the developer intended. \\
Experimental & Includes unsatisfied obligations. For instance,
forgetting to close a file. \\
Internationalization (i18n) & Indicates the use of non-localized methods. \\
Multi-Threaded ({\sc mt}) Correctness & Thread synchronization issues. \\
Performance & Involves inefficient memory usageallocation, usage 
of non-static classes. \\
Style & Code that is confusing, or
written in a way that leads to errors.\\
Malicious Code & Involves variables or fields exposed to classes that should
not be using them. \\
Security & Involves input validation issues, unauthorized database connections
and others. \\
\hline
\end{tabular}
\end{table}

Our findings can be analyzed at two levels. First, we discuss some
primary observations concerning the security bugs of the Maven repository as a whole.
Then, we provide a comprehensive analysis of the results and highlight our key findings.

@@

\begin{table*}
\centering
\caption{Number of Versions that Contain at Least One Severe Security Bug}
\label{tbl:sev}
\leavevmode
	\begin{tabular}{l r}
	\hline
	Bug Description & Number of Versions\\
 	\hline
	{\sc hrs}: {\sc http} cookie formed from untrusted input & 149\\
	{\sc hrs}: {\sc http} response splitting vulnerability & 1,564\\
	{\sc pt}: absolute path traversal in servlet  & 92\\
	{\sc pt}: relative path traversal in servlet & 50\\
	{\sc sql}: nonconstant string passed to execute method on an {\sc sql} & 1,817\\
	{\sc sql}: a prepared statement is generated from a nonconstant String & 1,438\\
	{\sc xss}: {\sc jsp} reflected cross site scripting vulnerability & 17\\
	{\sc xss}: Servlet reflected cross site scripting vulnerability in error page & 88\\
	{\sc xss}: Servlet reflected cross site scripting vulnerability & 140\\
	\hline
	\end{tabular}
\end{table*}

@@

As we mentioned earlier, during the experiment we managed to retrieve the
dependencies of every version. Based on this information we created a graph
that represented the snapshot of the Maven repository. The
nodes of the graph represented the versions and the vertices their dependencies.
We have to mention here that the graph was not representative. For instance, if
a dependency was pointing only to a project (and not to a specific version), we chose to
select the latest version found on the repository. Also, this graph is not
complete. This is because threre were missing versions.
% Practically, the corresponding {\it pom}, or {\it war} files existed on the
% repository, but the {\sc jar} file did not.
From the 56,5680 vertices, 191,433
belonged to the first case while 16,4234 belonged to the second.
The graph contained 80,354 nodes. Obviously, the number does not correspond to
the number of the total versions (see Section~\ref{sec:data}). This is because
some versions did not contain any information about their dependencies so they
are not represented in the graph. After creating the graph, we ran the PageRank
algorithm~\cite{BP98} on it and retrieved all PageRanks for every node. Then we
examined the security bugs of the fifty most popular nodes based on their PageRank.
Thirty three of them contained bugs coming from the {\it Security Low} subcategory,
while two of them contained severe bugs. Twenty five of them were latest
versions at the time.
% what can we say about this?

@@

\subsubsection{Persistense of Security Bugs}

@@

\begin{table}
    \centering
    \caption{Correlations between jarsize and Defects Count}
    \label{tbl:jarsizecorr}
    \input{jarsizecorr.tex}
\end{table}

@@

To see whether bugs flock together we performed pairwise correlations
between all bug categories. We calculated the correlations between the
number of distinct bugs that appeared in a project throughout its
lifetime. The results can be seen in Table~\ref{tbl:corrmatrix} and
Figure~\ref{fig:corrplot}. We found significant correlations between
all pairs apart from two pairs involving the {\it Security High}
category. In general, the {\it Security High} category showed the
weekest correlations with the other categories. Our results show that
in general bugs do flock together. We do not find projects with only a
certain kind of bug; bugs come upon projects in swarms of different
kinds. Bugs of the {\it Security High} category, though, are
different: they are either not associated with other bugs, or only
weakly so. Perhaps it takes a special kind of blunder to make it a
security hazard.

@@

There are numerous methods for mining software repositories in the context
of software evolution~\cite{KCM07}. In this section we focus on the ones
that highlight the relationship between software bugs and evolution and try to
extract useful conclusions. The key idea behind this concept is
similar to ours: the combination of information like bug decriptions,
documentation and others with the information retrieved from either the source
or object code of a project version.

@@

Using {\it micro patterns} is a method proposed by Kim et al.~\cite{KPW06}
to detect bug-prone patterns among source code. Micro patterns describe programming
idioms like inheritance, data management, immutability and others. The approach involved
the examination of all revisions of three open-source projects to extract bug
introduction rates for each pattern. Gil et al.~\cite{GM05} analyzed the
prevalence of micro patterns across five Sun {\sc jdk} versions to conclude that
pattern prevalence tends to be the same in software collections.

{\it Querying techniques} are used to answer a broad range of questions
regarding the evolution history of a project~\cite{HG05}. Bhattacharya et
al.~\cite{BN11}\cite{B11} proposed a framework that is based upon
recursively enumerable languages. The framework can correlate software
bugs with developers in various ways. For instanse, return the list of
bugs fixed by a specific developer. Fischer et al.~\cite{FPG03} proposed
an approach for populating a release history database that combines code
information with bug tracking data. In this way, a developer can couple files
that contain common bugs, estimate code maturity with respect to the bugs
and others. The ``Ultimate Debian Database''~\cite{NZ10} is an {\sc sql}-based
framework that integrates information about the Debian project from various
sources to answer queries related to software bugs and source code.

@@

The evolution of software artifacts has also been analyzed to {\it reduce the false
alarms} of the various static analysis tools. To achieve this, Spacco et
al.~\cite{SHP06} introduced {\it pairing} and {\it warning signatures}. In the
former, they tried to pair sets of bugs between versions in order to find
similar patterns. In the latter, they computed a signature for every bug. This
signature contained elemnts like the name of the class where the bug was found,
the method and others. Then they searched for similar signatures between
versions. In their research they also studied the evolution of 116 sequential
builds of the Sun Java Sevelopment Kit ({\sc jdk}). Their findings indicated that
high priority bugs are fixed over time. To improve the precision of bug
detection, Kim et al.~\cite{KE07b}\cite{KE07} proposed a history-based warning
prioritization algorithm by mining the history of bug-fixes of three
different projects. The algorithm was based on the following hypothesis: if a
bug that belongs to a specific category is eliminated by a code change, then
this warning category is important. Working towards the same direction, Heckman
et al.~\cite{HW09}\cite{HW08} have introduced benchmarks that use specific
correlation algorithms and classification techniques to evaluate alert
prioritization approaches.

Lu et al.~\cite{LAAL13} studied the {\it evolution of file-system code}.
Specifically, they analyzed the changes of Linux file-system patches to extract
bug patterns and categorize bugs based on their impact. Their findings
indicated that the number of file-system bugs does not die down over time. By
categorizing bugs they also showed the frequency of specific bugs in specific
components.

Contrary to the above, our work focuses on the subset of security bugs.
Focusing on such bugs is not a new idea. Massacci et al.~\cite{MNN11} observed
the evolution of software defects by examining six major versions of Firefox.
To achieve this they created a database schema that contained information
coming from the ``Mozilla Firefox-related Security Advisories'' ({\sc mfsa})
list,\footnote{\url{http://www.mozilla.org/projects/security/known-vulnerabilities.html}}
Bugzilla entries and others. Their findings indicated that security bugs are
persistent over time. They also showed that there are many web users that use
old versions of Firefox, meaning that old attacks will continue to work.
Zaman et al.~\cite{ZAH11} focused again on Firefox to study the relation of
security bugs with performance bugs. This was also done by analyzing the project's
Bugzilla. Their research showed that security bugs require more experienced developers
to be fixed. In addittion, they suggested that security bug fixes are more complex than the
fixes of performance and other bugs.
Shahzad et al.~\cite{SSL12} analyzed large sets of vulnerability data-sets to observe
various features of the vulnerabilities that they considered critical. Such features
were the functionality and the criticality of the defects. Their analysis
included the observation of vulnerability disclosures, the behavior of
hackers in releasing exploits for vulnerabilities, patching and others. In
their findings they highlighted the most exploited defects and showed that
the percentage of remotely exploitable vulnerabilities has gradually increased
over the years.

@@

\section*{Acknowledgments}

>>>>

\author{Dimitris Mitropoulos \and Vassilios Karakoidas \and Georgios Gousios \and Panos Louridas \and Diomidis Spinellis }
\institute{ Department of Management Science and Technology\\
			Athens University of Economics and Business\\
      		\email{\{dimitro, bkarak, louridas, dds\}@aueb.gr}\\
			Software Engineering Research Group\\
			Delft University of Technology\\
			\email{G.Gousios@tudelft.nl}}

@@

A security bug is a programming error that introduces a potentially
exploitable weakness into a computer system~\cite{SSL12}\cite{TJBD11}. This weakness could lead to a
security breach with unfortunate consequences in different layers, like databases,
native code, applications, libraries and others. Despite the significant
effort to detect and eliminate such bugs~\cite{SZ12}, little attention has been paid to
study them in relation to software evolution~\cite{L96}\cite{LRWPT97}\cite{IB06}\cite{RGMA06}.
In this paper we present how we used a large software ecosystem to analyse
how evolving software packages are related to the different types of security
vulnerabilities.

@@

We chose to focus our study on the security bugs rather than other
software bugs. This is because compared to other bug categories,
the category of security bugs has two distinct features: it is critical~\cite{SZ12}
and it costs~\cite{BCL08}. Specifically, a software bug can
lead to a malfunction of a software artifact that runs under specific
requirements but a security bug can allow a malicious user to alter the execution
of the entire application for his or her own gain. In this case, such bugs could span a wide
range of security and privacy issues, like viewing sensitive information, the destruction or
modification of sensitive data, denial of service and others.
Moreover, security bug disclosures lead to a negative and significant change
in market value for a software vendor~\cite{TW07}.
Hence, one of the basic pursuits in every new software release should
be the mitigation of such bugs.

The motivation behind our work was to validate if programmers tend to care for
such high-risk bugs when they release a new version of their software. In
addition, we wanted to investigate other critical features associated with such
vulnerabilities like the persistence of a bug. In essence, to check if critical bugs stay
unresolved for a long time. Also, we wanted to elaborate more on the relation of security
bugs not only with performance bugs (as Zaman et al.~\cite{ZAH11} have already
did) but also with other bug categories. In the same manner, we tried to check
the relation between a version's size and its' security bugs knowing the
that research has been contradictory on the the
issue~\cite{BP84}\cite{SYTP85}\cite{NBZ06}\cite{GKMS00}.
Finally, we examined the Maven ecosystem as a whole from a security
perspective. Its structure, gave us the opportunity to see if a project version that is a dependency to
a large number of others contains a high rate of security bugs.
In this case we can strengthen the relationship between Linus' Law and
software security as Meneely et al. have already indicated~\cite{MW10}.

The main contributions of this research are:
\begin{itemize}
	\item The analysis of how security bugs evolve over time. To achieve
this, we inspect every project per version. Our hypothesis is that security
bugs must decrease as a project evolves since they are critical and developers
should eliminate them.
	\item Security bug persistence between versions. We show evidence that
security bugs are not eliminated between versions.
	\item We show evidence of the relation between security bugs and a project
version's size.  Here, size is defined in terms of bytecode.
	\item The correlation of security bugs with other bug categories. We
show evidence on how such bugs are correlated with bugs that have to do with
performance, coding practices and others.
%	\item The relation of software dependencies and security bugs. Our
%hypothesis is that an artifact that is a dependency of many other artifacts
%should have a low rate of security bugs. 
\end{itemize}

@@

Initially, we obtained a snapshot (January 2012) of the Maven repository and
handled it locally to retrieve a list of all the names of the project versions
that existed in it. A project version can be uniquely identified by the triplet:
{\it group id}, {\it artifact id} and {\it version}.
Since FindBugs analyses applications written in the Java
programming language, and the Maven repository
hosts projects from languages other than Java such as Scala, Groovy,
Clojure etc. we filtered out such projects by performing a series of checks in
the repository data and metadata.

@@

The statistical measurements presented in Table~\ref{tbl:repository}
indicate that we have 17,505 projects and the data set's median
is 3, which means that almost 50\% (8,753 projects) of the project
population has 1 to 3 versions.
Note that the Maven repository has many projects with a
few number of versions. For instance, there are numerous projects with a
number of versions that is less than ten.
There are a few projects containing ten
versions and only a few with hundreds of versions. The maximum number of
versions for a project is 338. The 3$^{rd}$ quartile measurement
also indicated that 75\% (13,129) of the projects have a maximum of 8 versions.

@@

\begin{table}
\centering
\caption{Bug Categorisation According to FindBugs}
\label{tbl:bug-cat}
\begin{tabular}{l p{15em}}
\hline
Category & Description\\
\hline
Bad Practice & Violations of recommended and essential
coding practice. \\
Correctness & Involves coding mistakes resulting in code
that was probably not what the developer intended. \\
Experimental & Includes unsatisfied obligations. For instance,
forgetting to close a file. \\
Internationalization (i18n) & Indicates the use of non-localized methods. \\
Multi-Threaded ({\sc mt}) Correctness & Thread synchronization issues. \\
Performance & Involves inefficient memory usage allocation, usage 
of non-static classes. \\
Style & Code that is confusing, or
written in a way that leads to errors.\\
Malicious Code & Involves variables or fields exposed to classes that should
not be using them. \\
Security & Involves input validation issues, unauthorized database connections
and others. \\
\hline
\end{tabular}
\end{table}

Our findings can be analysed at two levels. First, we discuss some
primary observations concerning the security bugs of the Maven repository as a whole.
Then, we provide a comprehensive analysis of the results and highlight our key findings.

@@

\begin{table*}
\centering
\caption{Number of Versions that Contain at Least One Severe Security Bug}
\label{tbl:sev}
\leavevmode
	\begin{tabular}{l r}
	\hline
	Bug Description & Number of Versions\\
 	\hline
	{\sc hrs}: {\sc http} cookie formed from untrusted input & 149\\
	{\sc hrs}: {\sc http} response splitting vulnerability & 1,564\\
	{\sc pt}: absolute path traversal in servlet  & 92\\
	{\sc pt}: relative path traversal in servlet & 50\\
	{\sc sql}: non-constant string passed to execute method on an {\sc sql} & 1,817\\
	{\sc sql}: a prepared statement is generated from a non-constant String & 1,438\\
	{\sc xss}: {\sc jsp} reflected cross site scripting vulnerability & 17\\
	{\sc xss}: Servlet reflected cross site scripting vulnerability in error page & 88\\
	{\sc xss}: Servlet reflected cross site scripting vulnerability & 140\\
	\hline
	\end{tabular}
\end{table*}

@@

As we mentioned earlier, during the experiment we managed to retrieve the
dependencies of every version. Based on this information we created a graph
that represented the snapshot of the Maven repository. The
nodes of the graph represented the versions and the vertices their dependencies.
We have to mention here that the graph was not representative. For instance, if
a dependency was pointing only to a project (and not to a specific version), we chose to
select the latest version found on the repository. Also, this graph is not
complete. This is because there were missing versions.
% Practically, the corresponding {\it pom}, or {\it war} files existed on the
% repository, but the {\sc jar} file did not.
From the 56,5680 vertices, 191,433
belonged to the first case while 16,4234 belonged to the second.
The graph contained 80,354 nodes. Obviously, the number does not correspond to
the number of the total versions (see Section~\ref{sec:data}). This is because
some versions did not contain any information about their dependencies so they
are not represented in the graph. After creating the graph, we ran the PageRank
algorithm~\cite{BP98} on it and retrieved all PageRanks for every node. Then we
examined the security bugs of the fifty most popular nodes based on their PageRank.
Thirty three of them contained bugs coming from the {\it Security Low} subcategory,
while two of them contained severe bugs. Twenty five of them were latest
versions at the time.
% what can we say about this?

@@

\subsubsection{Persistence of Security Bugs}

@@

\begin{table}
    \centering
    \caption{Correlations between jar size and Defects Count}
    \label{tbl:jarsizecorr}
    \input{jarsizecorr.tex}
\end{table}

@@

To see whether bugs flock together we performed pairwise correlations
between all bug categories. We calculated the correlations between the
number of distinct bugs that appeared in a project throughout its
lifetime. The results can be seen in Table~\ref{tbl:corrmatrix} and
Figure~\ref{fig:corrplot}. We found significant correlations between
all pairs apart from two pairs involving the {\it Security High}
category. In general, the {\it Security High} category showed the
weakest correlations with the other categories. Our results show that
in general bugs do flock together. We do not find projects with only a
certain kind of bug; bugs come upon projects in swarms of different
kinds. Bugs of the {\it Security High} category, though, are
different: they are either not associated with other bugs, or only
weakly so. Perhaps it takes a special kind of blunder to make it a
security hazard.

@@

There are numerous methods for mining software repositories in the context
of software evolution~\cite{KCM07}. In this section we focus on the ones
that highlight the relationship between software bugs and evolution and try to
extract useful conclusions. The key idea behind this concept is
similar to ours: the combination of information like bug descriptions,
documentation and others with the information retrieved from either the source
or object code of a project version.

@@

Using {\it micro patterns} is a method proposed by Kim et al.~\cite{KPW06}
to detect bug-prone patterns among source code. Micro patterns describe programming
idioms like inheritance, data management, immutability and others. The approach involved
the examination of all revisions of three open-source projects to extract bug
introduction rates for each pattern. Gil et al.~\cite{GM05} analysed the
prevalence of micro patterns across five Sun {\sc jdk} versions to conclude that
pattern prevalence tends to be the same in software collections.

{\it Querying techniques} are used to answer a broad range of questions
regarding the evolution history of a project~\cite{HG05}. Bhattacharya et
al.~\cite{BN11}\cite{B11} proposed a framework that is based upon
recursively enumerable languages. The framework can correlate software
bugs with developers in various ways. For instance, return the list of
bugs fixed by a specific developer. Fischer et al.~\cite{FPG03} proposed
an approach for populating a release history database that combines code
information with bug tracking data. In this way, a developer can couple files
that contain common bugs, estimate code maturity with respect to the bugs
and others. The ``Ultimate Debian Database''~\cite{NZ10} is an {\sc sql}-based
framework that integrates information about the Debian project from various
sources to answer queries related to software bugs and source code.

@@

The evolution of software artifacts has also been analysed to {\it reduce the false
alarms} of the various static analysis tools. To achieve this, Spacco et
al.~\cite{SHP06} introduced {\it pairing} and {\it warning signatures}. In the
former, they tried to pair sets of bugs between versions in order to find
similar patterns. In the latter, they computed a signature for every bug. This
signature contained elements like the name of the class where the bug was found,
the method and others. Then they searched for similar signatures between
versions. In their research they also studied the evolution of 116 sequential
builds of the Sun Java Sevelopment Kit ({\sc jdk}). Their findings indicated that
high priority bugs are fixed over time. To improve the precision of bug
detection, Kim et al.~\cite{KE07b}\cite{KE07} proposed a history-based warning
prioritization algorithm by mining the history of bug-fixes of three
different projects. The algorithm was based on the following hypothesis: if a
bug that belongs to a specific category is eliminated by a code change, then
this warning category is important. Working towards the same direction, Heckman
et al.~\cite{HW09}\cite{HW08} have introduced benchmarks that use specific
correlation algorithms and classification techniques to evaluate alert
prioritization approaches.

Lu et al.~\cite{LAAL13} studied the {\it evolution of file-system code}.
Specifically, they analysed the changes of Linux file-system patches to extract
bug patterns and categorize bugs based on their impact. Their findings
indicated that the number of file-system bugs does not die down over time. By
categorizing bugs they also showed the frequency of specific bugs in specific
components.

Contrary to the above, our work focuses on the subset of security bugs.
Focusing on such bugs is not a new idea. Massacci et al.~\cite{MNN11} observed
the evolution of software defects by examining six major versions of Firefox.
To achieve this they created a database schema that contained information
coming from the ``Mozilla Firefox-related Security Advisories'' ({\sc mfsa})
list,\footnote{\url{http://www.mozilla.org/projects/security/known-vulnerabilities.html}}
Bugzilla entries and others. Their findings indicated that security bugs are
persistent over time. They also showed that there are many web users that use
old versions of Firefox, meaning that old attacks will continue to work.
Zaman et al.~\cite{ZAH11} focused again on Firefox to study the relation of
security bugs with performance bugs. This was also done by analysing the project's
Bugzilla. Their research showed that security bugs require more experienced developers
to be fixed. In addition, they suggested that security bug fixes are more complex than the
fixes of performance and other bugs.
Shahzad et al.~\cite{SSL12} analysed large sets of vulnerability data-sets to observe
various features of the vulnerabilities that they considered critical. Such features
were the functionality and the criticality of the defects. Their analysis
included the observation of vulnerability disclosures, the behavior of
hackers in releasing exploits for vulnerabilities, patching and others. In
their findings they highlighted the most exploited defects and showed that
the percentage of remotely exploitable vulnerabilities has gradually increased
over the years.

@@

\section*{Acknowledgements}
